Toxic Code Snippets on Stack Overflow

### 2018-11-28 cloverflow-tse/cloverflow.tex
Changed to past tense.
Updated the citation of Baltest et al. to EMSE paper and fixed the formatting of Qualitas project names to be consistent.

Although this activity of online code cloning is well-known, there are only a few
empirical studies on the topic~\cite{An2017,Abdalkareem2017,Baltes2017}, especially
on finding the origins of the clones on Q\&A websites.
In this study, we tackle this challenge of establishing the existence of online code 
clones on Stack Overflow, investigate how they occur, and study the potential
effects to software reusing them.
%Using the same analogy, in this study, we are interested in 
Therefore, we mine Stack Overflow posts, detected online code clones, and analysed the clones to reveal
``toxic code snippets.''

@@

Interestingly, we discovered that the buggy version of the
\texttt{humanReadableInt()} method from Hadoop appeared in two popular Java
projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854
stars and 1,946 forks). Due to the lack of evidence, we could not conclude how
this method, which is the same as the toxic code snippet we found on
Stack Overflow, appears in the two projects. It is possible that the developers
retrieved them from Stack Overflow, other websites, or from Hadoop code base
directly. Nevertheless, we reported them to the developers of the two projects
regarding the issue. We created a bug report for each project (deeplearning4j
\#4694\footnote{deeplearning4j bug report:
	\url{https://github.com/deeplearning4j/deeplearning4j/issues/4692}} and
HIVE-18929\footnote{Apache Hive bug report: \url{
		https://issues.apache.org/jira/browse/HIVE-18929}}) and communicated with the
developers of the projects by describing the problem of race condition in the
outdated version of the \texttt{humanReadableInt()} method and proposed a fix by
using the newest version of the method in Hadoop. The issue has been fixed in both projects.
The developers of deeplearning4j agreed that the method was
problematic and decided to implement their own fix due to a concern of a
potential software licensing conflict caused by copying the fix directly from
the Hadoop code base. The developers of Apache Hive found that the method is not used anywhere
in the project, so they decided to delete it.

@@

\textbf{Incompatible license:} there are 214 clone pairs which do not contain
licensing information after they are posted on Stack Overflow or contain a
different license from their Qualitas clone counterparts. Almost all (85) of
\textbf{QS} clone pairs have their licensing terms removed or changed when
posted on Stack Overflow. One QS clone pair posted by a JFreeChart developer
changed its license from Lesser GPL v2.1+ to New BSD 3-clause. The
developer may intentionally changed the license to be more suitable to Stack
Overflow since New BSD 3-clause license allows reuse without requiring the same
license in the distributing software or statement of changes.

@@

\begin{table}
	\centering
	\begin{tabular}{lrrrrr}
		\toprule
		\multirow{2}{*}{No. of stars} & \multicolumn{2}{c}{Qualitas} & \multicolumn{3}{c}{Other Projects} \\ \cmidrule{2-6}
		& Projects & Pairs & Projects & Pairs & Same license \\
		\midrule
		29,540--10 & 8 & 71 & 406 & 1,837 & 193 \\
		9--5 & 0 & 0 & 275 & 739 & 110 \\
		4--1 & 2 & 24 & 1,746 & 4,536 & 692 \\
		\midrule
		Total & 10 & 95 & 2,427 & 7,112 & 995 \\
		\bottomrule
	\end{tabular}
	\caption{Clones of the 214 Stack Overflow missing-license code snippets in 131,703 GitHub projects}
	\label{tab:license_github}
\end{table}

Note that the code snippets could potentially violate the license, but do
not necessarily do so. In the example where the JFreeChart
developer copied his own code, she or he was free to change the
license. The same may have occurred with any of the 214 code
snippets.

@@

\textbf{Automated cloning direction detection:} 
As shown in this study, we still relied on manual
validation to read the post, understand the context, and use multiple hints
based on human judgement (comments in the code, natural text in the question and
answers, date/time of the posts) to conclude that the code snippets are actually
copied from Qualitas or external sources to Stack Overflow. 
This is a burdensome and time-consuming process. We call for more research in
automation of code cloning direction detection. From our experience in this
paper, we found that code comments and accompanied natural text
on Stack Overflow were a great source of information to decide the direction of
code copying. Thus, by using code clone detection to locate clone candidates
and then applying information retrieval techniques, e.g.,~cosine similarity with tf-idf, 
we can rank the clone candidates based on the similarity of their project names (or classes) to the text in 
comments or natural text surrounding the clones in Stack Overflow posts.
For example, the Stack Overflow answer containing the text \textit{``Actually, you can learn how to compare in \textbf{Hadoop}
from \textbf{WritableComparator}. Here is an example that borrows some ideas from it.''}
must be ranked very high among the list of clone candidates of a code snippet
from Hadoop since it contains two terms of the project name (Hadoop) and a class name (WritableComparator)
in it.
This technique will dramatically reduce the manual validation effort to establish
the direction of cloning. The technique can also be used on Stack Overflow to 
flag that an answer has a high chance of copying from open source projects.

@@

Work similar to ours are studies by An et al.~\cite{An2017},
Abdalkareem et al.~\cite{Abdalkareem2017}, Baltes et al.~\cite{Baltes2017},
and~Zhang et al.~\cite{Zhang2018}. 
An et al.~investigated clones
between 399 Android apps and Stack Overflow posts. They found 1,226 code
snippets which were reused from 68 Android apps. They also observed that there
are 1,279 cases of potential license violations. The authors rely on the
timestamp to judge whether the code has been copied from/to Stack Overflow along
with confirmations from six developers. Instead of Android apps, we investigated
clones between Stack Overflow and 111 open source projects. Their results are
similar to our findings that there exist clones from software projects to Stack
Overflow with potential licensing violations. Abdalkareem et
al.~\cite{Abdalkareem2017} detected clones between Stack Overflow posts and
Android apps from the F-Droid repository and used timestamps to
determine the direction
of copying. They found 22 apps containing code cloned from Stack Overflow. They
reported that cloned code is commonly used for enhancing existing code. Their
analysis shows that the cloned code from Stack Overflow has detrimental effects on
quality of the apps. The median percentage of bug fixing commits after adding
Stack Overflow code (19.09\%) is higher than before adding the code (5.96\%)
with statistical significance.
Baltes et al.~\cite{Baltes2017} discovered that two-thirds of the clones 
from the 10 most frequently referenced Java code snippets on Stack
Overflow do not contain attributions.
Zhang et al.~\cite{Zhang2018} study quality of code snippets on
Stack Overflow.
They show that 31\% of the analysed Stack Overflow posts
contain potential API usage violations and could lead to program
crashes or resource leaks.
%Our study presents another findings that the Stack Overflow code snippets
%can be problematic due to being outdated or violating the original
%licenses.
%In our work, we defined seven patterns of online code cloning and 
%performed a large-scale manual check of 3,632 clone pairs. 
%We discovered 112 clone pairs with strong evidences, 
%based on natural text in comments and post contents, that they 
%were copied from Qualitas to Stack Overflow. By comparing the 
%clones to their latest versions in the software, we found that 
%64 code snippets on Stack Overflow are outdated and possibly harmful for reuse.

>>>>

Although this activity of online code cloning is well-known, there are only a few
empirical studies on the topic~\cite{An2017,Abdalkareem2017,Baltes2018}, especially
on finding the origins of the clones on Q\&A websites.
In this study, we tackle this challenge of establishing the existence of online code 
clones on Stack Overflow, investigate how they occur, and study the potential
effects to software reusing them.
%Using the same analogy, in this study, we are interested in 
Therefore, we mine Stack Overflow posts, detected online code clones, and analysed the clones to reveal
``toxic code snippets.''

@@

Interestingly, we discovered that the buggy version of the
\texttt{humanReadableInt()} method from \textsf{Hadoop} appeared in two popular Java
projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854
stars and 1,946 forks). Due to the lack of evidence, we could not conclude how
this method, which is the same as the toxic code snippet we found on
Stack Overflow, appears in the two projects. It is possible that the developers
retrieved them from Stack Overflow, other websites, or from \textsf{Hadoop} code base
directly. Nevertheless, we reported them to the developers of the two projects
regarding the issue. We created a bug report for each project (deeplearning4j
\#4694\footnote{deeplearning4j bug report:
	\url{https://github.com/deeplearning4j/deeplearning4j/issues/4692}} and
HIVE-18929\footnote{Apache Hive bug report: \url{
		https://issues.apache.org/jira/browse/HIVE-18929}}) and communicated with the
developers of the projects by describing the problem of race condition in the
outdated version of the \texttt{humanReadableInt()} method and proposed a fix by
using the newest version of the method in Hadoop. The issue has been fixed in both projects.
The developers of deeplearning4j agreed that the method was
problematic and decided to implement their own fix due to a concern of a
potential software licensing conflict caused by copying the fix directly from
the \textsf{Hadoop} code base. The developers of Apache Hive found that the method was not used anywhere
in the project, so they decided to delete it.

@@

\textbf{Incompatible license:} there are 214 clone pairs which do not contain
licensing information after they are posted on Stack Overflow or contain a
different license from their Qualitas clone counterparts. Almost all (85) of
\textbf{QS} clone pairs have their licensing terms removed or changed when
posted on Stack Overflow. One QS clone pair posted by a \textsf{JFreeChart} developer
changed its license from Lesser GPL v2.1+ to New BSD 3-clause. The
developer may intentionally changed the license to be more suitable to Stack
Overflow since New BSD 3-clause license allows reuse without requiring the same
license in the distributing software or statement of changes.

@@

\begin{table}
	\centering
	\begin{tabular}{lrrrrr}
		\toprule
		\multirow{2}{*}{No. of stars} & \multicolumn{2}{c}{Qualitas} & \multicolumn{3}{c}{Other Projects} \\ \cmidrule{2-6}
		& Projects & Pairs & Projects & Pairs & Same license \\
		\midrule
		29,540--10 & 8 & 71 & 406 & 1,837 & 193 \\
		9--5 & 0 & 0 & 275 & 739 & 110 \\
		4--1 & 2 & 24 & 1,746 & 4,536 & 692 \\
		\midrule
		Total & 10 & 95 & 2,427 & 7,112 & 995 \\
		\bottomrule
	\end{tabular}
	\caption{Clones of the 214 Stack Overflow missing-license code snippets in 130,719 GitHub projects}
	\label{tab:license_github}
\end{table}

Note that the code snippets could potentially violate the license, but do
not necessarily do so. In the example where the \textsf{JFreeChart}
developer copied his own code, she or he was free to change the
license. The same may have occurred with any of the 214 code
snippets.

@@

\textbf{Automated cloning direction detection:} 
As shown in this study, we still relied on manual
validation to read the post, understand the context, and use multiple hints
based on human judgement (e.g., comments in the code, natural text in the question and
answers, date/time of the posts) to conclude that the code snippets are actually
copied from Qualitas or external sources to Stack Overflow. 
This is a burdensome and time-consuming process. We call for more research in
automation of code cloning direction detection. From our experience in this
paper, we found that code comments and accompanied natural text
on Stack Overflow were a great source of information to decide the direction of
code copying. Thus, by using code clone detection to locate clone candidates
and then applying information retrieval techniques, e.g.,~cosine similarity with tf-idf, 
we can rank the clone candidates based on the similarity of their project names (or classes) to the text in 
comments or natural text surrounding the clones in Stack Overflow posts.
For example, the Stack Overflow answer containing the text \textit{``Actually, you can learn how to compare in \textbf{Hadoop}
from \textbf{WritableComparator}. Here is an example that borrows some ideas from it.''}
must be ranked very high among the list of clone candidates of a code snippet
from \textsf{Hadoop} since it contains two terms of the project name (Hadoop) and a class name (WritableComparator)
in it.
This technique will dramatically reduce the manual validation effort to establish
the direction of cloning. The technique can also be used on Stack Overflow to 
flag that an answer has a high chance of copying from open source projects.

@@

Work similar to ours are studies by An et al.~\cite{An2017},
Abdalkareem et al.~\cite{Abdalkareem2017}, Baltes et al.~\cite{Baltes2018},
and~Zhang et al.~\cite{Zhang2018}. 
An et al.~investigated clones
between 399 Android apps and Stack Overflow posts. They found 1,226 code
snippets which were reused from 68 Android apps. They also observed that there
are 1,279 cases of potential license violations. The authors rely on the
timestamp to judge whether the code has been copied from/to Stack Overflow along
with confirmations from six developers. Instead of Android apps, we investigated
clones between Stack Overflow and 111 open source projects. Their results are
similar to our findings that there exist clones from software projects to Stack
Overflow with potential licensing violations. Abdalkareem et
al.~\cite{Abdalkareem2017} detected clones between Stack Overflow posts and
Android apps from the F-Droid repository and used timestamps to
determine the direction
of copying. They found 22 apps containing code cloned from Stack Overflow. They
reported that cloned code is commonly used for enhancing existing code. Their
analysis shows that the cloned code from Stack Overflow has detrimental effects on
quality of the apps. The median percentage of bug fixing commits after adding
Stack Overflow code (19.09\%) is higher than before adding the code (5.96\%)
with statistical significance.
Baltes et al.~\cite{Baltes2018} discovered that only 23.2\% of the clones in GitHub projects
from the 10 most frequently referenced Java code snippets on Stack
Overflow contain attributions.
Zhang et al.~\cite{Zhang2018} study quality of code snippets on
Stack Overflow.
They show that 31\% of the analysed Stack Overflow posts
contain potential API usage violations and could lead to program
crashes or resource leaks.
%Our study presents another findings that the Stack Overflow code snippets
%can be problematic due to being outdated or violating the original
%licenses.
%In our work, we defined seven patterns of online code cloning and 
%performed a large-scale manual check of 3,632 clone pairs. 
%We discovered 112 clone pairs with strong evidences, 
%based on natural text in comments and post contents, that they 
%were copied from Qualitas to Stack Overflow. By comparing the 
%clones to their latest versions in the software, we found that 
%64 code snippets on Stack Overflow are outdated and possibly harmful for reuse.
